### 2014-02-01 thesis/src/chapters/chapter-design.tex
Thesis: drawing update

Cloud Self Adaptive Platform (Cloud-SAP) is a reference architecture aspiring to supply application providers with an autonomic computing environment. Figure \ref{img:architecture-context} shows Cloud-SAP place in an exemplary application provisioning request. 
\begin{figure}[!ht]
  \begin{center}
    \includegraphics[width=0.9\textwidth]{chapter-design/architecture-context}
  \end{center}
  \caption{Cloud-SAP place in an exemplary application provisioning request}
  \label{img:architecture-context}
\end{figure}

@@

\section{Overview}
The previous section dealt with all premises that led to a conclusion that the proposed architecture can rely heavily on the concept of an autonomic system. In this section the further elaboration on the solution is presented.
Figure \ref{img:architecture-context} showed the context which the architecture applies to. As one can see, Cloud-SAP can be seen as a proxy between the user and cloud instances and as a coordinator of the latter. Although cloud instance itself consists of a cloud manager and additional resources, in general, it is perfectly legitimate to consider it a resource as well.

@@

By means of manageability interface, external entities can control managed resources. It can be done by, e.g. leveraging API, configuration files or logs. Additionally, it is possible to obtain information via touchpoint about the state of the resource. \emph{Sensor} and \emph{effector} behaviours refers to mechanisms that allows collecting data and change the behaviour of the resource, respectively.

@@

Each autonomic manager implements the control loop which can be split into four consecutive blocks, which share knowledge among one another. The output from one block forms an input to another. However, it is perfectly possible for a block to perform an action for its side effects, e.g. an action can result in producing relevant information contained in log files, which, in turn, comprises a piece of shared knowledge. Each block implements different behaviour based on the abstraction level and resource they operate on (see figure \ref{img:csap-layered-structure}). Nevertheless it is possible to define their generic behaviour, which embraces the following phases that correspond to a given block:
\begin{itemize}
  \item \emph{monitor} -- this function of autonomic manager is responsible for collecting and aggregating data about the resource it manages,
  \item \emph{analyse} -- this part takes the data from \emph{monitor} phase and perform in-depth analysis of it, which can result in, e.g. prediction plans. It is possible to incorporate more complex mechanisms, such as machine-learning, to fully use the obtained information for better prediction models,
  \item \emph{plan} -- this block is responsible for planning the appropriate action based on the output of the previous block and policies,
  \item \emph{execute} -- the goal of this function of autonomic manager is to execute the planned action
\end{itemize}
What is more, an autonomic manager exposes \emph{sensor} and \emph{effector} manageability interfaces which enables other entities (including other autonomic managers) to manage it in a similar manner as the component itself manages a resource. The image of an autonomic manager with its control loop and provided interface is shown in figure \ref{img:autonomic-component}.

\begin{figure}[!ht]
  \begin{center}
    \includegraphics{chapter-design/autonomic-component}
  \end{center}
  \caption{Autonomic manager}
  \label{img:autonomic-component}
\end{figure}

>>>>

Cloud Self Adaptive Platform (Cloud-SAP) is a reference architecture aspiring to supply application providers with an autonomic computing environment. Figure \ref{img:csap-usage-context} shows Cloud-SAP place in an exemplary application provisioning request. 
\begin{figure}[!ht]
  \begin{center}
    \includegraphics[width=0.9\textwidth]{chapter-design/csap-usage-context}
  \end{center}
  \caption{Cloud-SAP place in an exemplary application provisioning request}
  \label{img:csap-usage-context}
\end{figure}

@@

\section{Overview}
The previous section dealt with all premises that led to a conclusion that the proposed architecture can rely heavily on the concept of an autonomic system. In this section the further elaboration on the solution is presented.
Figure \ref{img:csap-usage-context} showed the context which the architecture applies to. As one can see, Cloud-SAP can be seen as a proxy between the user and cloud instances and as a coordinator of the latter. Although cloud instance itself consists of a cloud manager and additional resources, in general, it is perfectly legitimate to consider it a resource as well.

@@

By means of manageability interface, external entities can control managed resources. It can be done by, e.g. leveraging API, configuration files or logs. Additionally, it is possible to obtain information via touchpoint about the state of the resource. \emph{Sensor} and \emph{effector} behaviours refers to mechanisms that allows collecting data and change the behaviour of the resource, respectively. Structure of touchpoint is shown in figure \ref{img:csap-touchpoint}.

\begin{figure}[!ht]
  \begin{center}
    \includegraphics[width=0.7\textwidth]{chapter-design/csap-touchpoint}
  \end{center}
  \caption{Touch point component}
  \label{img:csap-touchpoint}
\end{figure}

@@

Each autonomic manager implements the control loop which can be split into four consecutive blocks, which share knowledge among one another. The output from one block forms an input to another. However, it is perfectly possible for a block to perform an action for its side effects, e.g. an action can result in producing relevant information contained in log files, which, in turn, comprises a piece of shared knowledge. Each block implements different behaviour based on the abstraction level and resource they operate on (see figure \ref{img:csap-layered-structure}). Nevertheless it is possible to define their generic behaviour, which embraces the following phases that correspond to a given block:
\begin{itemize}
  \item \emph{monitor} -- this function of autonomic manager is responsible for collecting and aggregating data about the resource it manages,
  \item \emph{analyse} -- this part takes the data from \emph{monitor} phase and perform in-depth analysis of it, which can result in, e.g. prediction plans. It is possible to incorporate more complex mechanisms, such as machine-learning, to fully use the obtained information for better prediction models,
  \item \emph{plan} -- this block is responsible for planning the appropriate action based on the output of the previous block and policies,
  \item \emph{execute} -- the goal of this function of autonomic manager is to execute the planned action
\end{itemize}
What is more, an autonomic manager exposes \emph{sensor} and \emph{effector} manageability interfaces which enables other entities (including other autonomic managers) to manage it in a similar manner as the component itself manages a resource. The image of an autonomic manager with its control loop and provided interface is shown in figure \ref{img:csap-manager}.

\begin{figure}[!ht]
  \begin{center}
    \includegraphics[width=0.7\textwidth]{chapter-design/csap-manager}
  \end{center}
  \caption{Autonomic manager}
  \label{img:csap-manager}
\end{figure}
